\textbf{Political Instability and Financial Markets}

### 2017-08-22 doc/paper.tex
Updated abstract. Give this a read and see if you like the framing of the argument, description of the methodology, etc.

\singlespacing
\begin{abstract}
We examine the relationship between political instability and daily returns of national stock indices. Financial volatility increases dramatically following (and immediately before) ``irregular'' regime changes caused by coup d'etat, assassinations, and resignations. Some of the pre-resignation volatility occurs due to actions that precede the resignation such as public protests, riots, and popular demonstrations. However, these irregular regime changes have disparate effects on the direction of stock returns. Abnormal returns following resignations are large and positive (6\%) while abnormal returns following assassinations are negative and smaller in magnitude (1\%). The impact of coups tends to be negative, but some events such as the temporary ousting of Hugo Chavez during the 2002 Venezuelan coup attempt result in positive abnormal returns of 20\% or more.
\end{abstract}
\doublespacing

>>>>

\singlespacing
\begin{abstract}
We examine the relationship between political instability and daily returns of national stock indices. A common hypothesis is that political instability discourages investment and reduces economic growth. By contrast, we find that while financial volatility increases dramatically following ``irregular'' regime changes, different types of regime changes have disparate effects on stock returns. We use daily financial data and a constant mean return event study model to show that abnormal returns following resignations are large and positive (6\%), while abnormal returns following assassinations are negative and smaller in magnitude (1\%). The impact of coups tends to be negative, but some events such as the 2002 temporary ousting of Hugo Chavez in Venezuela result in positive abnormal returns of 20\% or more. We therefore find that the type of political event and its expected impact on economic policy determines the direction of abnormal returns.
\end{abstract}
\doublespacing
